Motorcycle Acceleration example

### 2018-11-06 analysis/motorcycle.Rmd
wflow_publish("motorcycle.Rmd")

Load the MASS, wavethresh, EbayesThresh and smashr packages. The MASS
package is loaded only for the Motorcycle Accident data. Some
additional functions are defined in `functions.motorcycle.R`.

@@

Note that the MASS and lattice packages are included in most standard
R installations.

@@

In this second plot, we compare the mean estimate provided by SMASH
(with heteroskedastic variances; orange line) against homoskedastic
SMASH (dotted magenta line), TI thresholding (dark blue line), and TI
thresholding when the variances have been estimated by SMASH (dotted
green line).

```{r plot-all-estimates, fig.height=5, fig.width=7}
plot(res.mc$x,res.mc$mu.est,type = "l",
     ylim = c(min(res.mc$y - 2 * sqrt(res.mc$var.est)),
              max(res.mc$y + 2 * sqrt(res.mc$var.est))),
	 xlab = "time (ms)",ylab = "acceleration (g)",lwd = 2,
	 col = "darkorange",xlim = c(0,60),xaxp = c(0,60,6))
lines(res.cons.mc$x,res.cons.mc$mu.est,lwd = 2,lty = "dotted",col = "magenta")
lines(res.ti.cons.mc$x,res.ti.cons.mc$mu.est,lwd = 2,lty = "solid",
      col = "darkblue")
lines(res.ti.mc$x,res.ti.mc$mu.est,lwd = 2,col = "limegreen",lty = "dotted")
points(res.mc$x,res.mc$y,pch = 1,cex = 0.8,col = "black")
```

>>>>

Load the MASS, lattice wavethresh, EbayesThresh and smashr
packages. The MASS package is loaded only for the Motorcycle Accident
data. Some additional functions are defined in
`functions.motorcycle.R`.

@@

Note that the MASS and lattice packages are included in most standard
R installations, so you probably don't need to install these packages
separately.

@@

In this second plot, we compare the mean estimate provided by SMASH
(with heteroskedastic variances; orange line) against homoskedastic
SMASH (dotted magenta line).

```{r plot-homo-smash-estimates, fig.height=5, fig.width=7}
plot(res.mc$x,res.mc$mu.est,type = "l",
     ylim = c(min(res.mc$y - 2 * sqrt(res.mc$var.est)),
              max(res.mc$y + 2 * sqrt(res.mc$var.est))),
	 xlab = "time (ms)",ylab = "acceleration (g)",lwd = 2,
	 col = "darkorange",xlim = c(0,60),xaxp = c(0,60,6))
lines(res.cons.mc$x,res.cons.mc$mu.est,lwd = 2,lty = "dotted",col = "magenta")
#  lines(res.ti.cons.mc$x,res.ti.cons.mc$mu.est,lwd = 2,lty = "solid",
#        col = "darkblue")
#  lines(res.ti.mc$x,res.ti.mc$mu.est,lwd = 2,col = "limegreen",lty = "dotted")
points(res.mc$x,res.mc$y,pch = 1,cex = 0.8,col = "black")
```

And in this next plot, we compare the SMASH estimates (orange line)
against the the mean estimates obtained by TI thresholding (dark blue
line), and TI thresholding when the variances have been estimated by
SMASH (dotted green line).

```{r plot-ti-thresh-estimates, fig.height=5, fig.width=7}
plot(res.mc$x,res.mc$mu.est,type = "l",
     ylim = c(min(res.mc$y - 2 * sqrt(res.mc$var.est)),
              max(res.mc$y + 2 * sqrt(res.mc$var.est))),
	 xlab = "time (ms)",ylab = "acceleration (g)",lwd = 2,
	 col = "darkorange",xlim = c(0,60),xaxp = c(0,60,6))
lines(res.ti.cons.mc$x,res.ti.cons.mc$mu.est,lwd = 2,lty = "solid",
      col = "darkblue")
lines(res.ti.mc$x,res.ti.mc$mu.est,lwd = 2,col = "limegreen",lty = "dotted")
points(res.mc$x,res.mc$y,pch = 1,cex = 0.8,col = "black")
```

*Add text here.*

[smash-github]: https://github.com/stephenslab/smash-paper
